---
title: "Financial data analysis"
author: "Fabrice Rossi"
format: html
---

```{r}
#| message: false
here::i_am("dplyr-102.Rproj")
library(here)
library(vroom) ## or readr
library(dplyr)
library(tidyr)
library(ggplot2)
```

## Data loading

```{r}
#| message: false
clients <- vroom(here("data", "client.csv"))
accounts <- vroom(here("data", "account.csv"))
disp <- vroom(here("data", "disp.csv"))
```

## Joining

```{r}
da <- inner_join(accounts, disp)
```

## Joining client

```{r}
cda <- inner_join(clients, da, by = join_by(client_id), suffix = c("_home", "_bank"))
```

### Home District versus Bank District

Because we saw discrepancies in the home and bank district, we can look at the extent.

```{r}
home_diff_bank <- cda |> filter(district_id_home != district_id_bank) |>
  nrow()
```

We observe that **`r home_diff_bank`** clients have a bank in another district compare to their where they live.

Now we can look at people who share an accoutn but don't live together
```{r}
cda |> 
  group_by(account_id) |> 
  distinct(district_id_home) |>
  summarise(N=n()) |> 
  filter(N>1) 
```

### Gender Gap
```{r}
clients |> count(gender) #gender balance
clients |>
  ggplot(aes(x=gender)) + geom_bar() + coord_flip() 
```
We can see that there is not much gender imbalance.

```{r}
cda |> 
  count(gender, type) |> 
  group_by(gender) |>
  mutate(freq=n/sum(n)) |>
  select(-n) |>
  pivot_wider(values_from = freq, names_from = type)
```

It seems first that there are no gender imbalance in despondent and owndership of bank account.

Influence of gender on despondent and owndership. 
```{r}
cda |>
  ggplot(aes(y=gender, fill=type)) + geom_bar(position = "fill")
```

```{r}
chisq.test(cda |> pull(gender),
           cda |> pull(type))
```

